---
title: "Lab 01 - Hello R"
author: "Fei Xie"
date: "02/03/2021"
output: github_document
---

## Load packages and data

```{r load-packages, message=FALSE}
library(tidyverse) 
library(datasauRus)
```

## Exercises

### Exercise 1

How many columns does the datasaurus_dozen file have? What are the variables included in the data frame? 

   dataset        n
 * <chr>      <int>
 1 away         142
 2 bullseye     142
 3 circle       142
 4 dino         142
 5 dots         142
 6 h_lines      142
 7 high_lines   142
 8 slant_down   142
 9 slant_up     142
10 star         142
11 v_lines      142
12 wide_lines   142
13 x_shape      142

### Exercise 2
Plot y vs. x for the dino dataset. Then, calculate the correlation coefficient between x and y for this dataset.

```{r plot-dino, fig.height=3, fig.width=6}
dino_data <- datasaurus_dozen %>%
  filter(dataset == "dino")

ggplot(data = dino_data, mapping = aes(x = x, y = y)) +
  geom_point()
```

```{r cor-dino}
dino_data %>%
  summarize(r = cor(x, y))
```

### Exercise 3
Plot y vs. x for the star dataset. Then, calculate the correlation coefficient between x and y for this dataset.

```{r plot-star, fig.height=3, fig.width=3}
star_data <- datasaurus_dozen %>%
  filter(dataset == "star")

ggplot(data = star_data, mapping = aes(x = x, y = y)) +
  geom_point()
```

```{r cor-star}
star_data %>%
  summarize(r = cor(x, y))
```

### Exercise 4

Plot y vs. x for the circle dataset. You can (and should) reuse code we introduced above, just replace the dataset name with the desired dataset. Then, calculate the correlation coefficient between x and y for this dataset. How does this value compare to the r of dino?

```{r plot-circle, fig.height= 3, fig.width=4}
circle_data <- datasaurus_dozen %>%
  filter(dataset == "circle")

ggplot(data = circle_data, mapping = aes(x = x, y = y))+ geom_point()

```

```{r cor-circle}
circle_data %>%
  summarize(r = cor (x,y))
```

### Exercise 5

Add code and narrative as needed.
To add R chunks either type out the backticks, curly braces, and the letter `r` or use the Insert chunk button above, green C+.
